### 2018-05-09 4_impl.tex
Finish considering Prof. Heljanko's comments, fix some mistakes in first 3 chapters.

The main call for commencing the work on \porthos[2] was the need for processing real-world C programs, which, at first, requires the input language to be extended.
This implies the support not only for new syntactic structures of C language (such as the \texttt{switch} statement or the postfix increment operator \texttt{i++}), but also for its fundamental concepts and features (such as types, pointer arithmetic or first-order functions), which requires revision of the whole architecture of the tool.
Yet far from all of the C language has been supported (that, considering its complexity and numerous pitfalls, goes far beyond current thesis%
\footnote{To ensure that, we have merely to look at existing C compilers, for instance, the open-source \texttt{gcc} compiler, which uses the C parser written in more than 18.5 thousand lines of code (see \url{https://github.com/gcc-mirror/gcc/blob/master/gcc/c/c-parser.c})}%
), we consider the accomplished work as a step towards this.
%This applies not only to instances that simply constitute the syntactic sugar of C language (such as the \texttt{switch} statement or the prefix increment operator \texttt{++i}), but also to its fundamental concepts and features (such as pointer arithmetic or structures).
%However, the architecture of current version of \porthos{} does not allow to ... as it is ....
% Although and optimisation of the tool so that it is able to process real C programs in perspective.

@@

@@

@@

@@

@@

>>>>

The main call for commencing the work on \porthos[2] was the need for processing real-world C programs, which, at first, requires the input language to be extended.
This implies the support not only for new syntactic structures of C language (such as the \texttt{switch} statement or the postfix increment operator \texttt{i++}), but also for its fundamental concepts and features (such as types, pointer arithmetic or first-order functions), which requires revision of the whole architecture of the tool.
Yet far from all of the C language has been supported (that, considering its complexity and numerous pitfalls, goes far beyond current thesis%
\footnote{For ensuring this, one merely has to look at existing C compilers, for instance, the open-source \tool{gcc} compiler, which uses the C parser written in more than 18.5 thousand lines of code (see \url{https://github.com/gcc-mirror/gcc/blob/master/gcc/c/c-parser.c})}%
), we consider the accomplished work as a step towards this.
%This applies not only to instances that simply constitute the syntactic sugar of C language (such as the \texttt{switch} statement or the prefix increment operator \texttt{++i}), but also to its fundamental concepts and features (such as pointer arithmetic or structures).
%However, the architecture of current version of \porthos{} does not allow to ... as it is ....
% Although and optimisation of the tool so that it is able to process real C programs in perspective.

@@

- carries the origin (text) -> all the origins can be resolved by the \texttt{LocationService} %todo: rename from CodeCitationService + create 3 instances for each of level. Or keep it for Y->text, and store references to the original Y-object by X-objects

@@

- carries the origin (Y)

@@

todo: rename everywhere assertions <- axioms

@@

carries the origin (X)

@@

%TODO: cite again here : alglave2018frightening + other Kernel references
